Title

### 2018-07-30 thesis/paper/paper.tex
Added allowed units

>>>>

\subsection{Allowed units (Q21514353)}
The allowed units constraint needs to determine inequality between all allowed units and each unit on a constrained statement. To this end the unit of a triple, qualifier or reference needs to be extracted during pre-processing. Three predicates unitTriple\([2]\), unitQualifier\([4]\) and unitReference\([4]\) are introduced. While each triple has a unique identifier and only need to associate this with the unit, qualifiers and references need to be identified completely to assign the correct unit.\\

Inequality between units needs to be determined if a constrained triple, qualifier or reference exists. For every allowed unit of the constraint the following rules are introduced
\begin{equation*}
\begin{split}
\text{req\_inequality}&(X, \text{allowedUnitConstant}) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{unitTriple}(S, X)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{req\_inequality}&(X, \text{allowedUnitConstant}) \leftarrow \\
&\text{qualifierEDB}(S, \text{propertyConstant}, V) \wedge \\
&\text{unitQualifier}(S, \text{propertyConstant}, V, X)
\end{split}
\end{equation*}
\begin{equation*}
\begin{split}
\text{req\_inequality}&(X, \text{allowedUnitConstant}) \leftarrow \\
&\text{referenceEDB}(S, \text{propertyConstant}, V) \wedge \\
&\text{unitReference}(S, \text{propertyConstant}, V, X)
\end{split}
\end{equation*}

The violations can then be found using the same premises with inequality added.
\todo[inline]{Kind of ridiculous to write basically the same premise repeatedly. Should probably write the general approach in demand-driven and just write the normal inequality here}
